### 2014-09-03 paper/main.tex
just a test to illustrate commit to Rick

\def\lfdr{\text{lfdr}}
\def\lfsr{\text{lfsr}}
\def\x{\mbf{x}}
\def\y{\mbf{y}}
\def\e{\mbf{e}}
\def\g{\mbf{g}}
\def\p{p}
\def\Yb{\hat{Y}_1^{\text{BAYES}}}
\def\Xperp{X_{1 \perp 0}}
\def\Pperp{P_{1 \perp 0}}
\def\Pperpb{\Pperp^{\text{B}}}
\def \hatd { \widehat{ d } }
\def \dhatin {\hatd^{\mbox{\tiny IN}}}
\def \dhatsw {\hatd^{\mbox{\tiny SW}}}
\def \mvn{\text{MVN}}
\def\mn{\text{MN}}
\def \iw{\text{W}^{-1}}
\def \fp {fastPHASE\ }
\def\var{\rm Var}
\def\mvr{\text{BMVR}}
\def\bfuni{\text{BF}_\text{uni}}
\def\one{\mbf{1}}
\def\zero{\mbf{0}}
\def\hall{H_{\text{all}}}
\def\pall{\p_{\text{all}}}
\def\bfall{\text{BF}_\text{all}}
\def\bfav{\text{BF}_\text{av}}
\def\gall{\gamma_\text{all}}
\def\limbfall{\bfall^\rightarrow}
\def\limbfav{\bfav^\rightarrow}
\def\limbfgamma{\BF_\gamma^\rightarrow}
\def\sxx{S_{xx}}
\def\syy{S_{yy}}
\def\vyy{V_{yy}}
\def\vyx{V_{yx}}
\def\vxx{{V_{xx}}}
\def\rss{\text{\rm RSS}}
\def\dss{\text{\rm $\Delta$SS}}
\def\U{U}
\def\D{D}
\def\I{I}
\def\luu{L_{UU}}
\def\indep{\perp}
\newcommand{\mbf}[1]{\mbox{\boldmath$#1$}} % true mathbf works in math
                                % mode too
\newcommand\height{{\it height}}
\newcommand\weight{{\it weight}}
\def\BF{\text{BF}}

@@

The initial goal of the ASH (Adaptive SHrinkage) project is to provide simple, generic, and flexible methods to derive ``shrinkage-based" estimates and credible intervals for unknown quantities $\beta=(\beta_1,\dots,\beta_J)$, given only estimates of those quantities ($\hat\beta=(\hat\beta_1,\dots, \hat\beta_J)$) and their corresponding estimated standard errors ($s=(s_1,\dots,s_J)$).

@@

By ``adaptive" shrinkage we 
have two key properties in mind. First, the appropriate amount of shrinkage is determined from the data, rather than being pre-specified. Second, the amount of shrinkage undergone by each $\hat\beta_j$ will depend on the standard error $s_j$: measurements with high standard error will undergo more shrinkage than measurements with low standard error.

@@

As an important special case, these methods address the "multiple comparisons" setting, where interest usually focuses on which $\beta_j$ can be confidently inferred to be non-zero. Such problems are usually tackled by computing a $p$ value for each $j$, often by applying a $t$ test to $\hat\beta_j/s_j$,
and then applying a generic procedure, such as that of Benjamini 
and Hochberg (1995?) or Storey (2001?), designed to control or
estimate the false discovery rate (FDR) or the positive FDR (Storey, 2001?). In essence we aim to provide analagous
generic methods that work directly with two numbers for each 
measurement $(\hat\beta_j,s_j$), rather than a single number (e.g.~ the $p$ value, or $t$ statistic). Working with these two numbers has two important benefits: first, it permits estimation and not only testing; second, the 
uncertainty in each measurement $\hat\beta_j$ can be more fully accounted for, reducing the impact of ``high-noise" measurements (large $s_j$) that can reduce the effectiveness of a standard FDR analysis.

@@

Suppose that we are interested in the values of $J$ ``effects" $\beta_j$ ($j=1,\dots,J$). In some contexts our interest may focus on which of the $\beta_j$ are ``significantly" different from zero, whereas in other contexts our interest may focus on estimating their values; the methods described here are suited to both these contexts.
 We assume that we have obtained data $D_1,\dots,D_J$ that provide independent estimates $\hat\beta_1,\dots,\hat\beta_J$ of these effects,
 with corresponding (estimated) standard errors $s_1,\dots,s_J$. For our purposes, these estimates and standard errors could be obtained from the data
 using any method, provided they (approximately) satisfy 
 \begin{equation} \label{eqn:betahat}
 \hat\beta_j | \beta_j, s_j \sim N(\beta_j, s_j).
 \end{equation}
 [In some settings a $t$ distribution assumption for $\hat\beta_j | s_j, \beta_j$ may be more appropriate, and could also be incorporated into our methods; see Discussion.]

A standard genomics analysis pipeline would first convert these numbers to a $Z$ score ($Z_j=\hat\beta_j/s_j$)
and a corresponding $p$ value ($p_j$), testing $H_j:\beta_j=0$.

Definition of FDR and lfdr (Bayesian); connection to frequentist definitions (Storey).

Then standard methods (e.g. the qvalue package) can be used
to estimate False Discovery Rates at any given threshold.

@@

The second issue is that directly modeling the p values, or z scores, say via non-parametric methods, without taking account of their precision, 
can lead to unrealistic distributions being fitted. Put another way, because z scores are the result of adding noise to some
distribution, the range of distributions they can take is limited Using entirely non-parametric methods loses this information.
The solution is to model beta hat as a convolution of some distribution g and an error component.

@@

 %(See Discussion for ideas on how our methods may be applicable more generally; for example if, in place of $s_j$, we have a $p$ value testing $\beta_j=0$.)

 In outline, we use a hierarchical model to combine information across measurements, with the aim of improving both accuracy and precision of estimates. 
 Specifically we assume that the effects $\beta_j$ are independent and identically distributed from some unknown distribution $g(\cdot)$,
 \begin{equation} \label{eqn:beta}
 \beta_j \sim g(\cdot),
 \end{equation}
 where $g$ will be estimated from
 the data.  Our methods make the following key assumptions, which distinguish them from most previous work in this area:
   \begin{enumerate}
  \item[A1:] The distribution $g(\cdot)$ is unimodal. (We assume here that the mode is at 0, although 
this could be relaxed.)  
 \item[A2:] The likelihood $L(\beta_j) := p(D_j | \beta_j)$ can be approximated by a normal likelihood,
 \begin{equation} \label{eqn:lik}
 \hat{L}_j(\beta_j) \propto \exp[-0.5(\beta_j-\hat\beta_j)^2/s_j^2].
 \end{equation}
%which, in light of (\ref{eqn:betahat}), is equivalent to
 % \begin{equation} \label{eqn:lik2}
% L(\beta_j) \propto p(\hat\beta_j | \beta_j, s_j).
 %\end{equation}
 \end{enumerate}

@@

Assumption A2 can derived from (\ref{eqn:betahat}) plus a couple of other assumptions. Specifically, assume that a) $\hat\beta_j, s_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$) and that b) $s_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\hat\beta_j, s_j | \beta) = p(\hat\beta | \beta, s_j) p(s_j | \beta)$, while the latter (b) suggests assuming that $p(s_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\hat\beta_j | \beta, s_j)$, which, with (\ref{eqn:betahat}),  implies A2. If $\hat\beta_j, s_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\hat\beta_j,s_j$, rather than conditional on $D_j$. See \cite{johnson.xx} and \cite{wakefield.xx} for more general discussion and examples of Bayesian inference based on summary statistics.

Alternatively A2 could be considered definitional for $\hat\beta_j,s_j$: that is, choose $\hat\beta_j,s_j$ such that A2 holds.

While Assumption A2 has parallels with approaches like \cite{efron, cai?} that model the $Z$ scores $Z_j = \hat\beta_j/s_j$ as normally distributed under the null, 
there is an important difference: here, observations with a large $s_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
other parameters, whereas when modeling the $Z$ scores directly, observations with large $s_j$ produce $Z$ scores with an $N(0,1)$ distribution that {\it do} affect inference. 
Because of this the likelihood-based approach can take better account of the informativeness of each measurement, as illustrated in Results below.

%The choice of normal likelihood seems natural, and indeed it can be motivated in multiple ways. For example, we can write $p(\hat\beta_j, s_j | \beta_j) = p(\hat\beta_j | s_j, \beta_j)p(s_j | \beta_j)$. Now, if we are willing to assume that $s_j$ alone contains no information about $\beta_j$, or equivalently that $p(s_j | \beta_j)$ does not depend on $\beta_j$, then $L(\beta_j) \propto p(\hat\beta_j | s_j, \beta_j)$, and if $\hat\beta_j | s_j, \beta_j \sim N(\beta_j, s_j^2)$, as is often asymptotically the case, then we obtain the likelihood (**) above.

@@

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any (asymmetric) unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $s_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

Further, the assumptions  $\hat\beta_j | \beta_j, s_j \sim N(\beta_j,s_j)$ and $\beta_j | s_j, \pi \sim g(\cdot; \pi)$ (given by \ref{eqn:g}) yield: 
\begin{equation}
p(\hat\beta_j, s_j | \pi) = \pi_0 N(\hat\beta_j; 0,s^2_j) + \sum_k \pi_k \tilde{f}_{kj}(\hat\beta_j)
\end{equation}
where $\tilde{f}_{kj}$ denotes the density of a convolution of $f_k$ with an $N(0,s^2_j)$ density.
For example, if $f_k(\cdot) = N(\cdot; 0,\sigma^2_k)$ then the convolution $\tilde{f}_{kj}$ is also normal, $\tilde{f}_{kj}(\cdot) = N(\cdot; 0,\sigma^2_k + s^2_j)$. If
$f_k(\cdot) = U[\cdot; a_k,b_k]$ then $\tilde{f}_{kj}$ is the convolution of a normal with a uniform, which has density
\begin{equation}
\tilde{f}_{kj}(x) = (\Phi(b_k/s_j) - \Phi(a_k/s_j))/(b-a),
\end{equation}
where $\Phi$ is the cumulative distribution function of the standard normal $N(0,1)$ distribution.

Putting these together, the joint model for the unobserved $\beta$ and the observed $\hat\beta, s$ is:
\begin{align}
p(\hat\beta, s, \beta | \pi) & = \prod_j g(\beta_j ; \pi) p(\hat\beta_j, s_j | \beta_j) \\
& = \prod_j g(\beta_j ; \pi) L(\beta_j; \hat\beta_j,s_j).
\end{align}

We fit this hierarchical model using the following "Empirical Bayes" approach. First we estimate the hyper-parameters $\pi$ by maximizing the likelihood
\begin{equation}
L(\pi; \hat\beta, s) := p(\hat\beta, s | \pi) = \int p(\hat\beta, s, \beta | \pi) d\beta.
\end{equation}
This can be done very easily using an EM algorithm.
Then, given this estimate $\hat\pi$, we compute the conditional distributions 
\begin{equation}
p(\beta_j | \hat\pi, \hat\beta, s) \propto g(\beta_j; \pi) L(\beta_j; \hat\beta_j, s_j).
\end{equation} 
In principle we would
prefer to take a full Bayes approach that accounts for uncertainty in $g$ (by accounting for uncertainty in $\pi$); however,
we believe that in most practical applications uncertainty in $g$ will not be the most important concern, and so 
we compromise this principle for the simplicity of the EB approach.
[Note: a Variational Bayes approach to estimating $\pi$ is also implemented in our R package]

@@

The conditional distributions $p(\beta_j | \hat\pi, \hat\beta, s)$ 
encapsulate uncertainty in the values for $\beta_j$, combining information across
$j=1,\dots,J$. The combining of the information occurs through estimation of
$\pi$, which involves all of the data.
These conditional distributions can be conveniently summarized
in various ways, including point estimates (e.g. the posterior means or medians),
and credible intervals/regions.

%A Taylor series expansion of the log likelihood around the maximum likelihood estimate $\hat\beta_j$  yields $$l(\beta_j) \approx l(\hat\beta_j) + 0.5* (\beta_j - \hat\beta_j)^2 l''(\hat\beta_j).$$ [Fill in details?]

@@

The local False Discovery Rate (lfdr) for observation $j$ is defined \cite{efron} as
\begin{equation}
\lfdr_j = p(\beta_j = 0 | \hat\pi, \hat\beta, s).
\end{equation}
The lfdr terminology comes from using "discovery" to refer to rejecting the null ($H_j:\beta_j=0$).
Specifically $\lfdr_j$ is the probability that, if we reject $H_j$,
it is a  "false discovery".

@@

Motivated by this, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\pi, \hat\beta, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05. We note that the idea of focussing on tail areas, rather than point null hypotheses,
has a long history (e.g. Altham? others?).

@@

As outlined above, we fit the model using the following Empirical Bayes procedure:
1. Estimate $\pi$ by maximizing the likelihood $L(\pi)$.
2. Compute the conditional distributions $p(\beta_j | \hat\beta_j, s_j, \hat\pi)$.

@@

For each simulation scenario we simulated 200 independent data sets. For each data set we simulated
the true value of $\pi_0  \sim U[0,1]$, and then simulated $\beta_j \sim \pi_0 \delta_0 + (1-\pi_0) f_1(\cdot)$
and $\hat\beta_j | \beta_j = N(\beta_j,1)$ for $j=1,\dots,n$. Thus these simulations assume the same
precision for each measurement. We applied the methods implemented in the R packages qvalue, fdrtool, locfdr, and mixfdr
for estimating $\pi_0$. We also applied our method to estimate $\pi_0$ in two ways, one using a penalty encourage
$\pi_0$ to be as large as possible (``null-biased"), and the other using the maximum likelihood estimate for $\pi$.

>>>>

\def\lfdr{\text{lfdr}}
\def\lfsr{\text{lfsr}}
\def\x{\mbf{x}}
\def\y{\mbf{y}}
\def\e{\mbf{e}}
\def\g{\mbf{g}}
\def\p{p}
\def\Yb{\hat{Y}_1^{\text{BAYES}}}
\def\Xperp{X_{1 \perp 0}}
\def\Pperp{P_{1 \perp 0}}
\def\Pperpb{\Pperp^{\text{B}}}
\def \hatd { \widehat{ d } }
\def \dhatin {\hatd^{\mbox{\tiny IN}}}
\def \dhatsw {\hatd^{\mbox{\tiny SW}}}
\def \mvn{\text{MVN}}
\def\mn{\text{MN}}
\def \iw{\text{W}^{-1}}
\def \fp {fastPHASE\ }
\def\bhat{\hat{\beta}}
\def\shat{\hat{s}}
\def\var{\rm Var}
\def\mvr{\text{BMVR}}
\def\bfuni{\text{BF}_\text{uni}}
\def\one{\mbf{1}}
\def\zero{\mbf{0}}
\def\hall{H_{\text{all}}}
\def\pall{\p_{\text{all}}}
\def\bfall{\text{BF}_\text{all}}
\def\bfav{\text{BF}_\text{av}}
\def\gall{\gamma_\text{all}}
\def\limbfall{\bfall^\rightarrow}
\def\limbfav{\bfav^\rightarrow}
\def\limbfgamma{\BF_\gamma^\rightarrow}
\def\sxx{S_{xx}}
\def\syy{S_{yy}}
\def\vyy{V_{yy}}
\def\vyx{V_{yx}}
\def\vxx{{V_{xx}}}
\def\rss{\text{\rm RSS}}
\def\dss{\text{\rm $\Delta$SS}}
\def\U{U}
\def\D{D}
\def\I{I}
\def\luu{L_{UU}}
\def\indep{\perp}
\newcommand{\mbf}[1]{\mbox{\boldmath$#1$}} % true mathbf works in math
                                % mode too
\newcommand\height{{\it height}}
\newcommand\weight{{\it weight}}
\def\BF{\text{BF}}

@@

The initial goal of the ASH (Adaptive SHrinkage) project is to provide simple, generic, and flexible methods to derive ``shrinkage-based" estimates and credible intervals for unknown quantities $\beta=(\beta_1,\dots,\beta_J)$, given only estimates of those quantities ($\bhat=(\bhat_1,\dots, \bhat_J)$) and their corresponding estimated standard errors ($s=(s_1,\dots,s_J)$).

@@

By ``adaptive" shrinkage we 
have two key properties in mind. First, the appropriate amount of shrinkage is determined from the data, rather than being pre-specified. Second, the amount of shrinkage undergone by each $\bhat_j$ will depend on the standard error $s_j$: measurements with high standard error will undergo more shrinkage than measurements with low standard error.

@@

As an important special case, these methods address the "multiple comparisons" setting, where interest usually focuses on which $\beta_j$ can be confidently inferred to be non-zero. Such problems are usually tackled by computing a $p$ value for each $j$, often by applying a $t$ test to $\bhat_j/s_j$,
and then applying a generic procedure, such as that of Benjamini 
and Hochberg (1995?) or Storey (2001?), designed to control or
estimate the false discovery rate (FDR) or the positive FDR (Storey, 2001?). In essence we aim to provide analagous
generic methods that work directly with two numbers for each 
measurement $(\bhat_j,s_j$), rather than a single number (e.g.~ the $p$ value, or $t$ statistic). Working with these two numbers has two important benefits: first, it permits estimation and not only testing; second, the 
uncertainty in each measurement $\bhat_j$ can be more fully accounted for, reducing the impact of ``high-noise" measurements (large $s_j$) that can reduce the effectiveness of a standard FDR analysis.

\def\df{df}
\def\FDR{\text{FDR}}
\def\fdr{\text{lfdr}}

@@

Suppose that we are interested in the values of $J$ ``effects" $\beta_j$ ($j=1,\dots,J$). In some contexts our interest may focus on which of the $\beta_j$ are ``significantly" different from zero, whereas in other contexts our interest may focus on estimating their values; the methods described here are suited to both these contexts.
 We assume that we have obtained data $D_1,\dots,D_J$ that provide independent estimates $\bhat_1,\dots,\bhat_J$ of these effects,
 with corresponding (estimated) standard errors $\shat_1,\dots,\shat_J$. For our purposes, these estimates and standard errors could be obtained from the data
 using any method, provided they (approximately) satisfy 
 \begin{equation} \label{eqn:betahat-t}
 \bhat_j \big{|} \, \beta_j, \shat_j \sim t_\nu(\beta_j,\shat_j),
 \end{equation}
for some known degrees of freedom (\df) $\nu$, where $t_\nu(\mu,\sigma)$ denotes the generalized $t$ distribution on $\nu$ \df, with mean $\mu$ and scale parameter $\sigma$. (Equivalently, $(\bhat_j-\beta_j)/\shat_j \big{|} \, \beta_j \sim t_\nu$, where $t_\nu$ denotes the standard $t$ distribution on $\nu$ \df.)
In the special case $\nu \rightarrow \infty$ this includes the situation where the $\bhat$ can be considered normally distributed:
  \begin{equation} \label{eqn:betahat-norm}
 \bhat_j  \big{|} \, \beta_j, \shat_j \sim N(\beta_j,\shat^2_j).
 \end{equation}
 Assuming (\ref{eqn:betahat-t}), the $t$-statistics defined by
 \begin{equation} 
 t_j:=\bhat_j/\shat_j
 \end{equation}
 have a $t_\nu$ distribution under the $j$th null hypothesis $H_j:\beta_j=0$, and this fact can be used to compute a $p$ value $p_j$ testing $H_j$.

One nice feature of the False Discovery Rate (FDR) is that Frequentist and Bayesian definitions are closely aligned.
Here we provide Bayesian definitions, and refer the reader to \cite{storey.03}, particularly his Theorem 1,  for connections with frequentist definitions.
The (tail) FDR at threshold $T$ is defined as
\begin{equation}
\FDR(T) := \Pr(\text{$H_j$ false} | t_j \geq T).
\end{equation}
The local FDR at $t$ is defined \cite{efron} as
\begin{equation}
\fdr(t) := \Pr(\text{$H_j$ is false} | t_j = t).
\end{equation}
The local FDR is perhaps more relevant than the tail FDR, but less widely used because
it is harder to estimate (density estimation is harder than tail area estimation). 
The $q$ value for observation $j$ is defined \cite{storey.03} as:
\begin{equation}
q_j := \FDR(t_j).
\end{equation}
That is, the $q$ value is the FDR if we reject the null for all observations that are at least as significant as $j$.

One standard genomics analysis pipeline is to take the $p$ values $p_1,\dots,p_J$ and convert them to (estimated) $q$ values $q_1,\dots,q_J$
 using the R package {\tt qvalue}. A graphical description of how {\tt qvalue} works is given in Figure \ref{}.

@@

The second issue is that directly modeling the p values, or z scores, say via non-parametric methods, 
can lead to unrealistic distributions being fitted. Put another way, because z scores are the result of adding noise to some
distribution, the range of distributions they can take is limited Using entirely non-parametric methods loses this information.
The solution is to model beta hat as a convolution of some distribution g and an error component.

@@

 %(See Discussion for ideas on how our methods may be applicable more generally; for example if, in place of $\shat_j$, we have a $p$ value testing $\beta_j=0$.)

 In outline, we use a hierarchical model to combine information across measurements, with the aim of improving both accuracy and precision of estimates. 
 Specifically we assume that the effects $\beta_j$ are independent and identically distributed from some unknown distribution $g(\cdot)$,
 \begin{equation} \label{eqn:beta}
 \beta_j \sim g(\cdot),
 \end{equation}
 where $g$ will be estimated from
 the data.  Our methods make the following key assumptions, which distinguish them from most previous work in this area:
   \begin{enumerate}
  \item[A1:] The distribution $g(\cdot)$ is unimodal. (We assume here that the mode is at 0, although 
this could be relaxed.)  
 \item[A2:] The likelihood $L(\beta_j) := p(D_j | \beta_j)$ can be approximated by a normal likelihood,
 \begin{equation} \label{eqn:lik}
 \hat{L}_j(\beta_j) \propto \exp[-0.5(\beta_j-\bhat_j)^2/\shat_j^2].
 \end{equation}
%which, in light of (\ref{eqn:betahat}), is equivalent to
 % \begin{equation} \label{eqn:lik2}
% L(\beta_j) \propto p(\bhat_j | \beta_j, \shat_j).
 %\end{equation}
 \end{enumerate}

@@

Assumption A2 can derived from (\ref{eqn:betahat}) plus a couple of other assumptions. Specifically, assume that a) $\bhat_j, \shat_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$) and that b) $\shat_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\bhat_j, \shat_j | \beta) = p(\bhat | \beta, \shat_j) p(\shat_j | \beta)$, while the latter (b) suggests assuming that $p(\shat_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\bhat_j | \beta, \shat_j)$, which, with (\ref{eqn:betahat}),  implies A2. If $\bhat_j, \shat_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\bhat_j,\shat_j$, rather than conditional on $D_j$. See \cite{johnson.xx} and \cite{wakefield.xx} for more general discussion and examples of Bayesian inference based on summary statistics.

Alternatively A2 could be considered definitional for $\bhat_j,\shat_j$: that is, choose $\bhat_j,\shat_j$ such that A2 holds.

While Assumption A2 has parallels with approaches like \cite{efron, cai?} that model the $Z$ scores $Z_j = \bhat_j/\shat_j$ as normally distributed under the null, 
there is an important difference: here, observations with a large $\shat_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
other parameters, whereas when modeling the $Z$ scores directly, observations with large $\shat_j$ produce $Z$ scores with an $N(0,1)$ distribution that {\it do} affect inference. 
Because of this the likelihood-based approach can take better account of the informativeness of each measurement, as illustrated in Results below.

%The choice of normal likelihood seems natural, and indeed it can be motivated in multiple ways. For example, we can write $p(\bhat_j, \shat_j | \beta_j) = p(\bhat_j | \shat_j, \beta_j)p(\shat_j | \beta_j)$. Now, if we are willing to assume that $\shat_j$ alone contains no information about $\beta_j$, or equivalently that $p(\shat_j | \beta_j)$ does not depend on $\beta_j$, then $L(\beta_j) \propto p(\bhat_j | \shat_j, \beta_j)$, and if $\bhat_j | \shat_j, \beta_j \sim N(\beta_j, \shat_j^2)$, as is often asymptotically the case, then we obtain the likelihood (**) above.

@@

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any (asymmetric) unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $\shat_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

Further, the assumptions  $\bhat_j | \beta_j, \shat_j \sim N(\beta_j,\shat_j)$ and $\beta_j | \shat_j, \pi \sim g(\cdot; \pi)$ (given by \ref{eqn:g}) yield: 
\begin{equation}
p(\bhat_j, \shat_j | \pi) = \pi_0 N(\bhat_j; 0,s^2_j) + \sum_k \pi_k \tilde{f}_{kj}(\bhat_j)
\end{equation}
where $\tilde{f}_{kj}$ denotes the density of a convolution of $f_k$ with an $N(0,s^2_j)$ density.
For example, if $f_k(\cdot) = N(\cdot; 0,\sigma^2_k)$ then the convolution $\tilde{f}_{kj}$ is also normal, $\tilde{f}_{kj}(\cdot) = N(\cdot; 0,\sigma^2_k + s^2_j)$. If
$f_k(\cdot) = U[\cdot; a_k,b_k]$ then $\tilde{f}_{kj}$ is the convolution of a normal with a uniform, which has density
\begin{equation}
\tilde{f}_{kj}(x) = (\Phi(b_k/\shat_j) - \Phi(a_k/\shat_j))/(b-a),
\end{equation}
where $\Phi$ is the cumulative distribution function of the standard normal $N(0,1)$ distribution.

Putting these together, the joint model for the unobserved $\beta$ and the observed $\bhat, s$ is:
\begin{align}
p(\bhat, s, \beta | \pi) & = \prod_j g(\beta_j ; \pi) p(\bhat_j, \shat_j | \beta_j) \\
& = \prod_j g(\beta_j ; \pi) L(\beta_j; \bhat_j,\shat_j).
\end{align}

We fit this hierarchical model using the following "Empirical Bayes" approach. First we estimate the hyper-parameters $\pi$ by maximizing the likelihood
\begin{equation}
L(\pi; \bhat, s) := p(\bhat, s | \pi) = \int p(\bhat, s, \beta | \pi) d\beta.
\end{equation}
This can be done very easily using an EM algorithm.
Then, given this estimate $\hat\pi$, we compute the conditional distributions 
\begin{equation}
p(\beta_j | \hat\pi, \bhat, s) \propto g(\beta_j; \pi) L(\beta_j; \bhat_j, \shat_j).
\end{equation} 
In principle we would
prefer to take a full Bayes approach that accounts for uncertainty in $g$ (by accounting for uncertainty in $\pi$); however,
we believe that in most practical applications uncertainty in $g$ will not be the most important concern, and so 
we compromise this principle for the simplicity of the EB approach.
[Note: a Variational Bayes approach to estimating $\pi$ is also implemented in our R package]

@@

The conditional distributions $p(\beta_j | \hat\pi, \bhat, s)$ 
encapsulate uncertainty in the values for $\beta_j$, combining information across
$j=1,\dots,J$. The combining of the information occurs through estimation of
$\pi$, which involves all of the data.
These conditional distributions can be conveniently summarized
in various ways, including point estimates (e.g. the posterior means or medians),
and credible intervals/regions.

%A Taylor series expansion of the log likelihood around the maximum likelihood estimate $\bhat_j$  yields $$l(\beta_j) \approx l(\bhat_j) + 0.5* (\beta_j - \bhat_j)^2 l''(\bhat_j).$$ [Fill in details?]

@@

The local False Discovery Rate (lfdr) for observation $j$ is defined \cite{efron} as
\begin{equation}
\lfdr_j = p(\beta_j = 0 | \hat\pi, \bhat, s).
\end{equation}
The lfdr terminology comes from using "discovery" to refer to rejecting the null ($H_j:\beta_j=0$).
Specifically $\lfdr_j$ is the probability that, if we reject $H_j$,
it is a  "false discovery".

@@

Motivated by this, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \bhat, s), p(\beta_j \leq 0| \hat\pi, \bhat, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \bhat, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05. We note that the idea of focussing on tail areas, rather than point null hypotheses,
has a long history (e.g. Altham? others?).

@@

As outlined above, we fit the model using the following Empirical Bayes procedure:
1. Estimate $\pi$ by maximizing the likelihood $L(\pi)$.
2. Compute the conditional distributions $p(\beta_j | \bhat_j, \shat_j, \hat\pi)$.

@@

For each simulation scenario we simulated 200 independent data sets. For each data set we simulated
the true value of $\pi_0  \sim U[0,1]$, and then simulated $\beta_j \sim \pi_0 \delta_0 + (1-\pi_0) f_1(\cdot)$
and $\bhat_j | \beta_j = N(\beta_j,1)$ for $j=1,\dots,n$. Thus these simulations assume the same
precision for each measurement. We applied the methods implemented in the R packages qvalue, fdrtool, locfdr, and mixfdr
for estimating $\pi_0$. We also applied our method to estimate $\pi_0$ in two ways, one using a penalty encourage
$\pi_0$ to be as large as possible (``null-biased"), and the other using the maximum likelihood estimate for $\pi$.
